---
title: "Responsibility and verification of AI-generated code in online discussions"
subtitle: "An exploratory study of five selected Hacker News discussions"
author: "Group 36"
student id:
  - "Dinh Trung Le - 22084424"
  - "Huynh Thanh Bach Phan - 22166214"
  - "Minh Duc Tran - 22084844"
date: "9 October 2026"
output:
  pdf_document:
    latex_engine: xelatex
    number_sections: true
    toc: true
    toc_depth: 3
    keep_tex: false
    includes:
      in_header: formatting/report-style.tex
    pandoc_args:
      - --lua-filter=formatting/report-layout.lua
  word_document:
    reference_docx: formatting/reference.docx
    number_sections: true
    toc: true
    toc_depth: 3
    fig_caption: true
    pandoc_args:
      - --lua-filter=formatting/report-layout.lua
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: kable
fontsize: 12pt
mainfont: Arial
sansfont: Arial
monofont: Arial
linestretch: 1.5
papersize: letter
geometry: "left=1.2in,right=1.2in,top=1in,bottom=1in"
bibliography: references.bib
link-citations: true
toc-title: "Table of Contents"
repository-url: "`r params$repository_url`"
group-members: "`r local({source('R/06_metadata.R', local=TRUE); paste(group_member_lines(read_group_metadata('docs/group_contributions.csv')), collapse=' ||| ')})`"
params:
  final_mode: false
  group_review_confirmed: false
  repository_url: "https://github.com/ledinhtrung05-coder/COMP3020-Group36"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = TRUE,
  fig.width = 7.0, fig.height = 4.0, fig.align = "center", fig.pos = "H",
  dpi = 160, out.width = "5.8333in", cache = FALSE)
options(width = 85)
needed <- c("here", "knitr", "cluster", "igraph")
missing <- needed[!vapply(needed, requireNamespace, logical(1), quietly = TRUE)]
if (length(missing)) stop("Run install_packages.R first. Missing: ", paste(missing, collapse = ", "))
here::i_am("Report_Group36_Integrated.Rmd")
project_root <- here::here()
for (script in c("00_data.R", "02_text_cluster.R", "03_hypothesis.R", "04_network.R", "05_export.R", "06_metadata.R")) {
  source(here::here("R", script), encoding = "UTF-8")
}
group_members <- read_group_metadata(here::here("docs", "group_contributions.csv"))
raw_path <- here::here("data", "raw", "hn_comments_raw.csv")
clean_path <- here::here("data", "processed", "hn_comments_clean.csv")
raw <- read_comments(raw_path)
comments <- read_comments(clean_path, clean = TRUE)
audit <- audit_comments(raw, comments)
text_result <- analyse_text(comments)
rq2 <- analyse_hypothesis(comments,
  here::here("data", "annotations", "verification_labels.csv"))
clusters <- analyse_clusters(comments, text_result)
clusters$sensitivity <- cluster_linkage_sensitivity(clusters)
network <- analyse_network(comments, seed = 3020)
bridge <- analyse_cluster_replies(comments, clusters$assignments)
results <- list(audit = audit, text = text_result, rq2 = rq2, clusters = clusters,
                network = network, bridge = bridge)
export_results(results, project_root)
save_project_figures(results, project_root)
net_value <- function(name) network$summary$value[match(name, network$summary$metric)]
short_text <- function(x, n = 150L) {
  x <- gsub("[\r\n]+", " ", as.character(x))
  ifelse(nchar(x) > n, paste0(substr(x, 1L, n), "..."), x)
}
show_table <- function(x, caption = NULL, digits = 3) {
  knitr::kable(x, format = "pipe", caption = caption, digits = digits, row.names = FALSE)
}
manifest <- read.csv(here::here("data", "collection_manifest.csv"),
  colClasses = "character", stringsAsFactors = FALSE, na.strings = c("", "NA"))
manifest_complete <- collection_manifest_complete(manifest, comments)
blockers <- character()
if (!rq2$row_labels_available) blockers <- c(blockers, "RQ2 comment-level labels are missing")
if (!manifest_complete) blockers <- c(blockers, "original collection provenance is incomplete")
if (!nzchar(trimws(params$repository_url))) blockers <- c(blockers, "repository URL has not been entered")
if (!group_metadata_complete(group_members)) blockers <- c(blockers, "three member names, unique student IDs and contribution percentages totalling 100% require confirmation")
if (!isTRUE(params$group_review_confirmed)) blockers <- c(blockers, "group review and interpretation are not yet confirmed")
if (isTRUE(params$final_mode) && length(blockers)) {
  stop("Final mode blocked: ", paste(blockers, collapse = "; "),
       ". Resolve these items; keep final_mode FALSE for a review render.")
}
```

```{r review-status, echo=FALSE, results='asis'}
if (!isTRUE(params$final_mode)) {
  cat("**Review version.** The computations below run from the supplied files. This is not a submission-ready claim. Outstanding items: ",
      paste(blockers, collapse = "; "), ".\n\n", sep = "")
}
```

# Research purpose and design

## Rationale

AI-assisted programming makes verification a substantive concern. A 24-participant study identified difficulties understanding and debugging generated suggestions [@vaithilingam2022]. @barke2023 distinguished examination, execution, static analysis and documentation lookup. These concepts motivate examining verification language; they do not validate our dictionary or establish practice prevalence.

Here, **responsibility** means expressed expectations about who should understand, check, approve or remain answerable for code. GitHub's provider guidance recommends reviewing and validating suggestions [@githubcopilot]. Reported confidence can nevertheless differ from observed verification success [@obrien2025]. We therefore study expressed discussion and reply activity, not actual workplace behaviour or code quality.

Related discourse research includes @agarwal2026, a preprint proposing an explanatory theory whose causal propositions remain untested. Our contribution is a bounded connection between text, an exploratory association, lexical clusters and observed reply relationships, rather than a claim of discovering a new phenomenon.

## Connected research questions {.page-break}

**Overall question:** How are responsibility and verification of AI-generated code discussed online, and how are these discussions structured through reply interactions?

| Question | Analytical contribution |
|:--|:--|
| RQ1. What responsibilities and verification practices are discussed in relation to AI-generated code? | Describe words and candidate mentions; interpret examples in context. |
| RQ2. Is mentioning at least one specific code-verification practice associated with whether a comment receives a direct reply? | Test a comment-level association using the teammate's supplied labels. |
| RQ3. What content clusters emerge, and which aspects of responsibility or verification characterise them? | Assess whether lexical groups support meaningful themes. |
| RQ4. Which participants and content clusters receive replies, and how are reply interactions structured? | Analyse the author network and connect replies to receiving-comment clusters. |

: Connected research questions and analytical contributions

RQ1 motivates examining practice mentions and replies in RQ2; RQ3 checks thematic structure before RQ4 links content with interactions. RQ2 replaces the earlier reading-versus-testing proposal with the teammate's completed question. RQ4 retains the teammate's structural analysis and adds the content bridge. These revisions are explicit; the design was not preregistered.

# Data, collection and analytical boundaries

## Source and collection provenance

The group confirms collecting the data using R on **`r paste(format(as.Date(unique(manifest$original_collection_date)), '%d %B %Y'), collapse=', ')`**; the exact time and timezone are unavailable. The recovered collector uses `jsonlite::fromJSON` and the official Hacker News item endpoint, traversing `kids` from five fixed story IDs. It retains IDs, parents, authors, Unix times, HTML text, availability flags and story titles. The API supports text analysis and reconstruction of observed reply links [@hnapi].

**Sample rationale.** The five supplied discussions address independent review, verification costs, automated checking and human validation of AI-generated code. These topics connect the verification concerns in @vaithilingam2022 and @barke2023 to our questions about responsibility and replies. This explains the corpus's relevance; it is not a reconstruction of unrecorded search queries, screening counts or exclusion decisions. The sample is bounded and non-probability, not an exhaustive platform survey.

The archived collector and cleaner document implementation; Git dates are not collection dates. The original collector has no request log or retry mechanism, so missing items and later replies remain unobserved. The separate collection guide records each thread's relevance and source limitations. Knit uses the frozen CSVs; the optional collector creates a separate new snapshot.

```{r data-loading-code, eval=FALSE}
raw <- read_comments(here::here("data", "raw", "hn_comments_raw.csv"))
comments <- read_comments(
  here::here("data", "processed", "hn_comments_clean.csv"), clean = TRUE)
audit <- audit_comments(raw, comments)
```

## Cleaning audit and sample composition {.page-break}

The recovered cleaner removes dead/deleted comments, strips HTML tags, decodes specified entities, collapses whitespace and converts times to UTC. The integrated audit checks IDs, unchanged shared fields and the retained-reply definition without replacing the supplied clean text.

```{r audit-summary, echo=FALSE}
keep <- c("Raw comments", "Clean comments", "Removed dead", "Removed deleted",
          "Threads", "Clean authors", "Authors with multiple comments")
show_table(audit$summary[audit$summary$metric %in% keep, ],
           "Data and reply-definition audit", digits = 0)
```

Removed IDs `r if (audit$removed_exactly_dead_deleted) "are exactly the dead/deleted records" else "require exclusion review"`; retained shared fields are unchanged. Unique IDs and matched raw parents establish internal consistency, not collection completeness. The full audit is exported.

::: {.page-break}
::: 

```{r thread-composition, echo=FALSE}
thread_display <- audit$threads[, c("thread_id", "title", "raw_n", "clean_n", "authors")]
thread_display$title <- short_text(thread_display$title, 66)
names(thread_display) <- c("Thread ID", "Thread title", "Raw", "Clean", "Authors")
show_table(thread_display, "Selected discussions; author counts are not additive across threads", 0)
```

Comment timestamps span `r format(min(comments$created_utc), "%d %B %Y", tz="UTC")` to `r format(max(comments$created_utc), "%d %B %Y", tz="UTC")`; this is not continuous coverage. The three largest threads contribute `r fmt_pct(sum(sort(table(comments$thread_id), decreasing=TRUE)[1:3]) / nrow(comments))` of comments. Selection is not a probability sample of Hacker News or programmers.

## Variables and units {.page-break}

| Variable or object | Definition and unit |
|:--|:--|
| Comment, thread and parent IDs | Character keys; joins use IDs, never row positions. |
| `text` / `text_raw` | Clean display text / preserved HTML source. |
| `received_reply` | At least one direct child retained in the clean corpus. |
| `verification_specific` | Supplied specific-practice label; separate from the dictionary. |
| Candidate indicators | Non-exclusive lexical matches, not validated attitudes. |
| Text cluster | Assignment of an eligible comment, not an author's position. |
| Author edge | Replying author to the retained parent-comment author. |

: Analytical variables and units

Using raw child IDs changes `r nrow(audit$reply_definition_changes)` retained comment's reply flag. We consistently use clean children. Removed, later or uncollected replies are unobserved, rather than proof that no reply ever occurred. Root stories are absent, so story-level replies do not become author edges.

# Research question

## RQ1: responsibility and verification in the text {.unnumbered}

### Representation and descriptive measures {.unnumbered}

We lowercase ASCII text, remove URLs, expand common contractions and keep alphabetic tokens of at least two characters. A frozen English stopword list retains negators. Unstemmed words remain readable but split related forms. Quoted material is retained because flattened boundaries cannot reliably identify quote-only text.

```{r rq1-code, eval=FALSE}
text_result <- analyse_text(comments)
head(text_result$frequencies, 20)
```

```{r rq1-frequent-words, echo=FALSE, fig.height=4.7, fig.cap='Frequent retained words. Counts include quotations and describe occurrences, not people or endorsement.'}
plot_text_frequencies(text_result)
```

The leading terms are `r paste(head(text_result$frequencies$term, 6), collapse=", ")`. Frequency identifies visible vocabulary, not responsibility, endorsement or effectiveness. Contextual validation remains necessary [@grimmer2013].

```{r rq1-candidate-mentions, echo=FALSE, fig.height=3.5, fig.cap='Comments matching each dictionary indicator. Categories overlap; matches may be quoted, negated or critical.'}
plot_candidate_mentions(text_result)
```

The indicators adapt verification concepts and add responsibility/formal-verification language. Exact patterns and matches are exported. These are screening counts: criticism can mention testing, while implicit practices may be missed. The dictionary does not create RQ2 labels.

### Contextual reading: what the indicators can and cannot mean {.unnumbered .page-break}

Four purposively selected examples illustrate meaning, not representative qualitative coding. Full text remains traceable by ID.

| Comment ID | Contextual interpretation |
|:--|:--|
| 43862722 | Human ownership of AI-generated pull requests restores identifiable responsibility and independent review. |
| 43867077 | Making approvers responsible for fixes could discourage helpful reviewers: responsibility is contested. |
| 43863986 | Property-based testing requires defining properties before generating test inputs. |
| 43862230 | Sarcasm about regenerating inconvenient tests shows why testing words do not imply endorsement. |

: Contextual examples of responsibility and verification

RQ1 therefore identifies human ownership, review independence and concrete checking practices, alongside disagreement about responsibility. These selected examples come from one discussion; they establish presence, not corpus-wide prevalence. RQ2 separately asks whether specific-practice mentions are associated with replies, which may express interest, clarification or disagreement.

## RQ2: specific verification mentions and direct replies {.unnumbered .page-break}

### Question, measurement and hypotheses {.unnumbered}

**H0:** specific-practice mentions and retained direct replies are independent. **H1:** they are associated, without a specified direction. The reference significance level is 0.05.

The group reports creating the labels using code in Excel. The source definition of TRUE is a mention of a specific way to check or test AI-generated code. The recovered R script assigns TRUE to 123 listed IDs and FALSE otherwise, exactly reproducing the supplied labels. The original Excel expression has not been inspected, so its handling of quotations and ambiguous cases is unverified. Labels are preserved; the dictionary is not their source.

```{r rq2-main-code, eval=FALSE}
rq2 <- analyse_hypothesis(comments,
  here::here("data", "annotations", "verification_labels.csv"))
chisq.test(rq2$table, correct = TRUE)
```

```{r rq2-observed-table, echo=FALSE}
tab_display <- rq2$rates
tab_display$reply_rate <- 100 * tab_display$reply_rate
names(tab_display) <- c("Specific practice", "No reply", "Reply", "Total", "Reply percent")
show_table(tab_display, "Specific verification mention and retained direct reply", 1)
```

All `r nrow(rq2$annotations)` labels join by `comment_id`, with shared fields checked. Comment 47290993 is FALSE despite discussing review; 43862196 is TRUE for a challenged quoted-review claim. These require rule clarification, not silent recoding. Matching the original table verifies arithmetic, not coding validity.

### Test and interpretation {.unnumbered .page-break}

Two binary variables produce a 2-by-2 count table. Pearson's chi-square is the association test under an independent-comment reference model; Yates' correction is explicit [@rchisq].

```{r rq2-result, echo=FALSE}
expected_display <- data.frame(Specific_practice = rownames(rq2$expected),
  No_reply = rq2$expected[, "FALSE"], Reply = rq2$expected[, "TRUE"])
names(expected_display) <- c("Specific practice", "No reply", "Reply")
show_table(expected_display, "Expected cell counts under independence", 2)
```

All expected counts exceed five (minimum `r fmt_num(min(rq2$expected), 2)`), but this **does not establish independence**. There are `r sum(table(comments$author) > 1)` repeat-contribution authors and `r nrow(audit$threads)` nested discussions. Neither Fisher's test nor a Monte Carlo p-value would remove this dependence.

```{r rq2-rate-plot, echo=FALSE, fig.height=3.0, fig.cap='Observed retained-reply proportions from supplied labels. Denominators are comments; reply does not imply agreement.'}
plot_reply_rates(rq2)
```

The reference test gives $\chi^2$ = `r fmt_num(unname(rq2$test$statistic), 4)`, df = 1, p = `r fmt_num(rq2$test$p.value, 4)`. Rates are `r fmt_pct(rq2$rates$reply_rate[2])` for TRUE and `r fmt_pct(rq2$rates$reply_rate[1])` for FALSE: a `r fmt_num(rq2$difference_pp, 2)` percentage-point difference.

```{r rq2-conditional-conclusion, echo=FALSE, results='asis'}
if (rq2$test$p.value >= 0.05) {
  cat("The reference model does not reject H0. This is not evidence of equivalence or no relationship.\n\n")
} else {
  cat("The reference p-value is below 0.05, but dependence prevents treating it alone as reliable population evidence.\n\n")
}
```

Effect size and design matter beyond a significance label [@asa2016]. Timing, visibility and text length are uncontrolled. This exploratory result is neither causal nor generalisable to all programmers.

### Descriptive check by discussion {.unnumbered}

```{r rq2-by-thread, echo=FALSE}
thread_rates <- rq2$by_thread[, c("thread_id", "no_practice_n", "no_practice_reply_rate",
                                 "specific_n", "specific_reply_rate")]
thread_rates$no_practice_reply_rate <- ifelse(is.na(thread_rates$no_practice_reply_rate),
  "n/a", fmt_pct(thread_rates$no_practice_reply_rate))
thread_rates$specific_reply_rate <- ifelse(is.na(thread_rates$specific_reply_rate),
  "n/a", fmt_pct(thread_rates$specific_reply_rate))
names(thread_rates) <- c("Thread", "FALSE n", "FALSE reply %", "TRUE n", "TRUE reply %")
show_table(thread_rates, "Reply proportions within each thread and supplied label; n/a means no comments in that category", 0)
```

One category is absent in `r sum(rq2$by_thread$no_practice_n == 0 | rq2$by_thread$specific_n == 0)` thread(s). Its rate is unavailable, not zero. Uneven denominators help explain the pooled composition; this breakdown does not adjust for dependence.

## RQ3: exploratory content clusters {.unnumbered .page-break}

### Representation, distance and selection rule {.unnumbered}

For clustering only, broad terms `r paste(clusters$settings$domain_stopwords, collapse=", ")` are removed. Comments need five retained tokens; vocabulary must occur in at least two documents and at most 80% of eligible documents. Empty vectors are excluded. These pragmatic cutoffs limit sparse features; excluded comments remain in the reply network.

Nonzero TF is $1+\log(c_{dt})$, IDF is $\log(N/df_t)$, followed by L2 normalisation. Cosine dissimilarity $1-x_i^Tx_j$ compares vocabulary profiles with reduced raw-length effects [@manning2008]. Authors, threads and reply outcomes are not input features.

```{r rq3-code, eval=FALSE}
clusters <- analyse_clusters(comments, text_result)
clusters$sensitivity <- cluster_linkage_sensitivity(clusters)
```

Average linkage groups comments by mean pairwise dissimilarity. Among k = 2–8, we maximise mean silhouette subject to at least five comments per cluster. If none passes, the highest silhouette is a **diagnostic fallback**, not a validated optimum. Silhouette contrasts within-cluster and nearest-other-cluster dissimilarity [@rsilhouette].

```{r rq3-diagnostic-plot, echo=FALSE, fig.height=2.8, fig.cap='Separation and minimum-size diagnostics. Crosses fail the five-comment guard; the filled marker shows the declared selection.'}
plot_cluster_diagnostics(clusters)
```

There are `r clusters$settings$n_clustered` eligible comments and `r clusters$settings$n_terms` terms; `r clusters$settings$n_excluded` comments are unassigned. Selected k = `r clusters$selected_k`, mean silhouette = `r fmt_num(clusters$settings$selected_mean_silhouette, 4)`. `r clusters$settings$selection_reason`

```{r rq3-dendrogram, echo=FALSE, fig.height=2.8, fig.cap='Average-link hierarchy with selected cut. Rectangles indicate lexical partitions, not social groups.'}
plot_cluster_dendrogram(clusters)
```

### Cluster profiles and contextual checks {.unnumbered .page-break}

```{r rq3-profile-table, echo=FALSE}
profile <- clusters$cluster_summary[, c("cluster", "n_comments", "mean_silhouette", "median_retained_tokens", "top_terms")]
names(profile) <- c("Group", "n", "Mean silhouette", "Median tokens", "Top terms")
show_table(profile, "Exploratory profiles; top terms are descriptors, not validated theme names", 3)
```

The medoid minimises mean within-cluster dissimilarity; the boundary example has the lowest silhouette. Their complete texts and IDs are exported for inspection.

```{r rq3-context-reading, echo=FALSE, results='asis'}
assignment <- stats::setNames(clusters$assignments$cluster,
                              clusters$assignments$comment_id)
tiny <- assignment[c("43877106", "47289697")]
large <- assignment[c("47290376", "47295857")]
if (all(!is.na(c(tiny, large))) && tiny[1] == tiny[2] &&
    large[1] == large[2] && tiny[1] != large[1] &&
    sum(assignment == tiny[1], na.rm = TRUE) == 2L) {
  cat("**Cluster ", large[1], " is a heterogeneous remainder.** Its medoid (47290376) questions specifications and unit tests while discussing simulation and human review. Boundary comment 47295857 advocates test-driven development. Shared review/testing words therefore cover different arguments.\n\n", sep = "")
  cat("**Cluster ", tiny[1], " is a two-comment lexical pairing.** Comment 43877106 links specification-driven and test-driven design as 'hand in hand'; 47289697 contrasts disposable generated code with 'hand crafted' code. The common word *hand* has different meanings. This is not a coherent verification theme.\n\n", sep = "")
} else {
  cat("The assignments differ from the reviewed snapshot. Re-read the exported medoid and boundary texts before assigning themes.\n\n")
}
```

```{r rq3-quality-reading, echo=FALSE, results='asis'}
if (clusters$settings$used_fallback || clusters$settings$selected_mean_silhouette < 0.05) {
  cat("**The primary representation does not support well-separated, balanced thematic clusters.** We report a diagnostic partition without inventing stance labels.\n\n")
} else {
  cat("Numerical separation alone does not validate themes; contextual reading remains necessary.\n\n")
}
```

Median length, thread composition and complete examples remain exported. They diagnose interpretation rather than establish semantic validity. Relevance was not manually coded, so contextual or promotional material can remain.

### Sensitivity to linkage {.unnumbered .page-break}

Complete linkage uses the same cosine dissimilarity; Ward.D2 uses Euclidean distance between the L2-normalised vectors. Each applies the same k range and size guard. Ward is not applied directly to cosine distances.

```{r rq3-sensitivity, echo=FALSE}
sensitivity_selected <- clusters$sensitivity[clusters$sensitivity$selected_within_method, ]
show_table(sensitivity_selected[, c("method", "k", "mean_silhouette", "sizes", "admissible")],
  "Selected diagnostic partition within each linkage/distance specification", 4)
```

Complete linkage's selected silhouette is `r fmt_num(sensitivity_selected$mean_silhouette[sensitivity_selected$method == "complete_cosine"], 4)`; Ward's is `r fmt_num(sensitivity_selected$mean_silhouette[sensitivity_selected$method == "ward_euclidean"], 4)`. `r if (all(sensitivity_selected$mean_silhouette < 0.05)) "Neither alternative gives convincing separation. Changing linkage does not rescue a strong thematic interpretation." else "The alternatives require contextual assessment before any thematic interpretation."` Different distance scales prevent treating this as an algorithm leaderboard. Better-delimited documents and validated content labels are future work, not grounds to select a preferred conclusion now.

## RQ4: direct-reply structure and the content bridge {.unnumbered .page-break}

### Network construction {.unnumbered}

Nodes are authors participating in retained between-author replies. A directed edge A to B means A replied to B's comment. Repeated ordered pairs collapse into one edge with separate event frequency. Self-replies are excluded (`r net_value("Self-reply events")` here).

```{r rq4-code, eval=FALSE}
network <- analyse_network(comments, seed = 3020)
igraph::degree(network$graph, mode = "in", loops = FALSE)
igraph::betweenness(network$graph, directed = TRUE,
                    weights = NA, normalized = TRUE)
```

```{r rq4-network-summary, echo=FALSE}
keep <- c("Network authors", "Unique directed author pairs", "Density",
          "Weak components", "Largest weak component", "Strong components")
network_display <- network$summary[network$summary$metric %in% keep, ]
network_display$value <- ifelse(network_display$metric == "Density",
  fmt_num(network_display$value, 4), as.character(as.integer(network_display$value)))
names(network_display) <- c("Metric", "Value")
show_table(network_display, "Directed author network properties")
```

The graph combines `r net_value("Matched reply events")` matched events. It excludes `r net_value("Authors outside graph")` other clean-corpus authors, `r sum(audit$parent_type == "root_story")` story replies and `r sum(audit$parent_type == "removed_or_missing_parent")` replies to unavailable parents. Adding excluded authors as isolates would change density and normalised centrality.

### Whole network and justified subgraph {.unnumbered}

```{r rq4-full-network, echo=FALSE, fig.height=5.0, fig.cap='Full author reply network. Arrows run from replying author to parent author. Seeded positions do not encode semantic similarity.'}
plot_network_full(network)
```

```{r rq4-largest-component, echo=FALSE, fig.height=5.0, fig.cap='Largest weak component: the largest connected author set when direction is ignored. Labels identify selected high-in-degree authors.'}
plot_network_lcc(network, label_count = 6)
```

The largest weak component contains `r net_value("Largest weak component")` authors (`r fmt_pct(net_value("Largest weak component share"))` of the graph). The largest strong component has only `r net_value("Largest strong component")`, so weak connectivity is not reciprocal exchange. Pooling threads can connect repeat participants without making them one conversation or establishing consensus. The degree distribution is exported.

### Centrality and interpretation {.unnumbered .page-break}

In-degree counts distinct replying authors; incoming strength counts reply events. Betweenness measures directed shortest-path positions, normalised across the full graph. It is **unweighted**: reply frequency is not a distance [@igraphbetween].

```{r rq4-centrality, echo=FALSE}
centrality_display <- head(network$node_metrics[, c("author", "indegree", "instrength", "betweenness")], 8)
names(centrality_display) <- c("Author", "In-degree", "Reply events received", "Normalised betweenness")
show_table(centrality_display, "Participants ranked by in-degree, then betweenness", 4)
```

`r paste(head(network$node_metrics$author, 2), collapse=" and ")` lead in-degree (`r paste(head(network$node_metrics$indegree, 2), collapse=" and ")`). Their betweenness values are `r paste(formatC(head(network$node_metrics$betweenness, 2), digits=4, format="f"), collapse=" and ")`: receiving attention and linking directed paths are different roles. Neither proves expertise, agreement or causal influence. These calculations reproduce the teammate PDF's principal numerical findings; reconstructed code and originals remain separately identified.

### Which content receives replies? {.unnumbered .page-break}

Clusters join to **receiving parent comments** by `comment_id`. An author can write across clusters. Unassigned child comments still count as replies to an assigned parent.

```{r rq4-bridge-code, eval=FALSE}
bridge <- analyse_cluster_replies(comments, clusters$assignments)
```

```{r rq4-bridge-table, echo=FALSE}
bridge_display <- bridge$receiver_rates
bridge_display$reply_rate <- 100 * bridge_display$reply_rate
names(bridge_display) <- c("Receiver cluster", "Comments", "Comments with reply", "Reply percent", "Incoming reply events")
show_table(bridge_display, "Descriptive reply outcomes by receiving-comment cluster", 1)
```

This connects content and interaction without assigning one theme to each author. Weak clustering limits its substantive meaning: a rate based on only two lexically paired comments cannot establish whether a theme attracts replies. No extra significance test is performed. The exported sender-by-receiver matrix requires both labels and reports excluded-event coverage.

# Overall findings, limitations and conclusion

Human ownership, independent review and checking practices appear together, but contextual examples contest how responsibility should be allocated. Specific-practice mentions receive retained replies at `r fmt_pct(rq2$rates$reply_rate[2])`, versus `r fmt_pct(rq2$rates$reply_rate[1])` otherwise (difference `r fmt_num(rq2$difference_pp, 2)` percentage points; reference p = `r fmt_num(rq2$test$p.value, 4)`). This provides no basis for claiming that concrete verification language reliably increases attention.

Clustering selects k = `r clusters$selected_k` with sizes `r paste(clusters$cluster_summary$n_comments, collapse="/")` and mean silhouette `r fmt_num(clusters$settings$selected_mean_silhouette, 4)`. `r if (clusters$settings$used_fallback || clusters$settings$selected_mean_silhouette < 0.05) "The partition does not establish distinct, balanced themes, restricting interpretation of cluster reply rates." else "The lexical profiles still require contextual validation."` Meanwhile, the observed network is sparse (density `r fmt_num(net_value("Density"), 4)`), yet `r net_value("Largest weak component")` of `r net_value("Network authors")` authors share its largest weak component. Attention concentrates on particular reply targets, without implying influence or consensus.

The conclusion concerns **expressed responsibility and retained interactions**, not the best practice or code quality. Five selected, uneven threads restrict generalisation; exact search and request logs are unavailable. The uninspected Excel rule, ambiguous labels, quoted language, dependent comments and unequal time to receive replies limit measurement and inference. Sparse vocabulary limits clustering; omitted parents and edge-only author selection constrain the network. Reviewed labels and broader documented sampling should precede stronger claims.

# Reproducibility and group contributions

Relative paths, frozen UTF-8 files, character IDs, explicit logical parsing and UTC dates support consistent runs. Validation reloads disk inputs and rejects missing/mismatched IDs. No API request occurs during Knit. Installation and recollection are separate steps.

The teammate's RQ2 question, labels and test are preserved; RQ4's principal network results are reproduced, with added content linkage. Original submissions and recovered repository scripts are archived. New RQ1/RQ3 modules and integration decisions remain identifiable. The originals use historical paths and are evidence files, not scripts to source during the integrated run.

The repository includes complete functions, data, run instructions and exported tables/figures. Appendix A gives core operations; `outputs/session_info.txt` records the environment. Actual contributions belong in `docs/group_contributions.csv`.

**AI assistance and group evaluation:** AI supported source research, code development and draft review. The group's own critical evaluation, interpretation and understanding remain required. Group members must verify the executed outputs and be able to explain the complete project at the poster discussion; no unperformed human review is claimed.

# Appendix A: core analytical operations {.unnumbered}

These excerpts show the central calculations. Full functions add the documented filters, joins and validation; versions are recorded in `outputs/session_info.txt`.

```{r appendix-tfidf-core, eval=FALSE}
tf <- counts
tf[counts > 0] <- 1 + log(counts[counts > 0])
idf <- log(nrow(counts) / colSums(counts > 0))
tfidf <- sweep(tf, 2, idf, "*")
tfidf <- tfidf / sqrt(rowSums(tfidf^2))
d <- 1 - tcrossprod(tfidf)
d[d < 0] <- 0
diag(d) <- 0
tree <- hclust(as.dist(d), method = "average")
groups <- cutree(tree, k = selected_k)
cluster::silhouette(groups, as.dist(d))
```

```{r appendix-network-core, eval=FALSE}
# author_edges contains matched, non-self ordered pairs and event frequency
g <- igraph::graph_from_data_frame(author_edges, directed = TRUE)
igraph::degree(g, mode = "in", loops = FALSE)
igraph::betweenness(g, directed = TRUE, weights = NA, normalized = TRUE)
```

# References {-}
